Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-06 paper/main.tex
linear vs cubic comparison added. report modified

\def\b0{{\bf 0}}
\def\ba{{\bf a}}
\def\bb{{\bf b}}
\def\bc{{\bf c}}
\def\bd{{\bf d}}
\def\be{{\bf e}}
\def\bg{{\bf g}}
\def\bh{{\bf h}}
\def\bi{{\bf i}}
\def\bj{{\bf j}}
\def\bk{{\bf k}}
\def\bl{{\bf l}}
\def\bm{{\bf m}}
\def\bn{{\bf n}}
\def\bo{{\bf o}}
\def\bp{{\bf p}}
\def\bq{{\bf q}}
\def\br{{\bf r}}
\def\bs{{\bf s}}
\def\bt{{\bf t}}
\def\bu{{\bf u}}
\def\bv{{\bf v}}
\def\bw{{\bf w}}
\def\bx{{\bf x}}
\def\by{{\bf y}}
\def\bz{{\bf z}}

\def\bSigma{{\bf \Sigma}}
\def\bA{{\bf A}}
\def\bB{{\bf B}}
\def\bC{{\bf C}}
\def\bD{{\bf D}}
\def\bE{{\bf E}}
\def\bF{{\bf F}}
\def\bG{{\bf G}}
\def\bH{{\bf H}}
\def\bI{{\bf I}}
\def\bJ{{\bf J}}
\def\bK{{\bf K}}
\def\bL{{\bf L}}
\def\bM{{\bf M}}
\def\bN{{\bf N}}
\def\bO{{\bf O}}
\def\bP{{\bf P}}
\def\bQ{{\bf Q}}
\def\bR{{\bf R}}
\def\bS{{\bf S}}
\def\bT{{\bf T}}
\def\bU{{\bf U}}
\def\bV{{\bf V}}
\def\bW{{\bf W}}
\def\bX{{\bf X}}
\def\bY{{\bf Y}}
\def\bZ{{\bf Z}}

%package list
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

% \usepackage{parskip}
% \setlength{\parskip}{0.02\baselineskip}

% \fancypagestyle{plain}{
%   \fancyhf{} % sets both header and footer to nothing
% \renewcommand{\headrulewidth}{0pt}
%   \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}% Right header

% }
\pagestyle{plain}% Set page style to plain.

% \pagestyle{fancyplain}
% \fancyhf{}
% \renewcommand{\headrulewidth}{0pt}
% \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}
\DeclareMathOperator*{\argmin}{argmin}
% \usepackage{titlesec}

% \titlespacing*{\section}{0pt}{1pt plus 2p}{1ex}
% \titleformat*{\section}{\fontsize{12}{12}\bfseries}
% \titleformat{\section}
%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries}{\thesection}{1em}{}

% \titleformat{\subsection}
%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries\itshape}{\thesubsection}{1em}{}

\begin{document}
%Here goes the title

@@

 \author{\authorblockN{Author 1, Author 2, Author 3}
 \
 \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle

\thispagestyle{plain}
%Main body starts

% \noindent We consider problem of quantization and interpolation of
% time and frequency varying precoding matrices in wireless MIMO
\begin{abstract}
In a limited feedback MIMO channel, the performance of the channel can improve significantly if the transmitter knows the channel state information(CSI). The receiver knows the channel information, and it feeds back to the transmitter. However, it is not possible to feedback complete information for a limited-feedback OFDM channel since the channel information for multiple subcarriers consumes a large amount of data. Therefore to resolve this problem, the orthonormality structure of the precoder matrix is exploited to make its one-to-one mapping to a minimal number of scalar parameters. The Precoder matrix is decomposed using Givens Rotation. For an i.i.d. flat-fading Rayleigh channel, these parameters are independent, which makes its quantization and interpolation easy. We propose an efficient method for quantization of the channel state information at the receiver by using adaptive delta modulation for successive time interval. We also propose a method for joint time-frequency interpolation of the channel information at the transmitter. 153-words
\end{abstract}

@@

The use of multiple antennas at the transmitter and receiver can significantly enhance the performance of wireless systems. Moreover, in these multiple-input multiple-output (MIMO) wireless systems, the transmitter can perform better resource allocation if channel state information (CSI) is made available at the transmitter, both to improve data rates and reduce BER~\cite{love2008overview}. To this end, feeding back the CSI from the receiver to the transmitter efficiently is necessary. In wireless systems that use orthogonal frequency division multiplexing (OFDM), the feedback needs to be provided to the transmitter across all subcarriers, and this places a large feedback demand. However, since the CSI varies gradually in both time and frequency, effective techniques to reduce feedback overheads exist, using frequency domain interpolation temporal prediction. In particular, knowledge of the precoding matrices (that are typically the orthonormal right singular vectors of the channel matrix) is essential to achieve link capacity, as well as to parallelize the channel. In this paper, we focus on the problem of tracking the precoders of a MIMO-OFDM system across time and frequency for efficient CSI feedback.

The problem of effective quantization and feedback of precoders for MIMO-OFDM has attracted significant attention in recent years. Many approaches involve codebook design over the Grassmann manifold~\cite{mondal2007quantization,schwarz2013adaptive,5946308} or the Stiefel Manifold \cite{6891198,Gupt1905:Predictive}, wherein the manifold structure of the precoders is used to obtain tangents for predictive quantization and interpolation across time and frequency. While these methods have been shown to be very effective for precoder feedback,  they involve operations over higher dimensional manifolds. In particular, optimization and interpolation is complicated, especially for manifolds where geodesic paths for interpolation may be difficult to obtain, especially for joint time-frequency predictive coding. An alternate approach is to parametrize the precoding matrices using scalar parameters. The space of unitary matrices parameterized into independent scalar parameters that correspond to Givens rotations and Household Transformations of the unitary precoding matrices \cite{4114278,4556174}. These approaches have been combined with adaptive delta modulation effectively track precoding matrices both in the time~\cite{4114278} and frequency domains~\cite{4556174}, albeit separately.

In this paper, we propose a method for exploiting the joint time-frequency correlation of the precoder's scalar parameters on the transmitter using CSI feedback. Typical approaches to predictive quantization and interpolation do not exploit the joint time-frequency correlation to enhance the precoder estimate at the transmitter. However, exploiting the correlations jointly not only reduces the feedback requirement, it also is able to enhance the precoder reconstruction accuracy. Further, the independence of the scalar parameters reduces the problem to interpolation of separate scalar valued function, as opposed to operations over tangent spaces in manifolds~\cite{Gupt1905:Predictive}. Simulations reveal that the proposed method offers matches the performance of manifold based approaches with a much lower implementation complexity and fewer number of bits.

The rest of this paper is organized as follows: Section~\ref{section2} described the system model and the precoder feedback and interpolation techniques. Section~\ref{section3} compares the BER and achievable rates for our proposed methods with that of past work. Finally, Section~\ref{section4} concludes with discussions on future work.

@@

\begin{equation}
\by_{i,t} = \bH_{i,t} \bx_{i,t}+ \bf{\eta_{i,t}}
\end{equation}

@@

where the channel matrix $\bH_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $\bx_{i,t} \in \mathbb{C}^{N_T}$; the output $\by_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $\bH_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_R}$, $\Sigma_{i,t} \in \mathbb{C}^{N_R \times N_R}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_R}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

% Givens rotation definition and how we are decomposing, Theta- pdf = 2lsin(theta)(2l-1).\cos(theta) 0 $\leq$ Theta $\leq$ pi/2.
% Householders' transformation and how we are decomposing. -pi$\leq$ phi $\leq$ pi. Uniformly distributed.
% Low-complexity quantization scheme based on a further parameterization of a vector in
% terms of a minimal number of independent scalar parameters. In particular, we consider its application to CSI feedback in slowly time-varying MIMO channels

@@

I_{m-2} & & & \\
& \cos\;\theta & - \sin\;\theta & \\
& \sin\;\theta & \cos\;\theta & \\
& & & I_{t-m}

@@

\begin{figure}
\label{adpm-fig}
%\includegraphics[width=0.45\textwidth]{images/new-adpm-crop.pdf}
\caption{Subcarriers which need to be quantized}
\label{ber_overvie}
\vspace{-5pt}
\end{figure}

@@

\begin{equation}
p(\theta) = 2l\sin(\theta)^{2l-1}\cos(\theta), \theta \in [0, \frac{\pi}{2}), for \; l = 1,2,\ldots,t-1
\end{equation}

@@

\begin{equation}
\label{delta_eqn}
\Delta_{n} = \begin{cases}
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}.\\
    \Delta_{n-1}/m , & \text{if $\beta_{n} \neq \beta_{n-1}$}.
  \end{cases}
\end{equation}

@@

We need to quantize the subcarriers in a way such that we can exploit
the joint time-frequency interpolation at the transmitter
side. Therefore, we select the subcarriers for quantization in an
alternating fashion as shown in the figure. Figure shows a \textbf{N}
subcarrier MIMO channel with subcarriers which are going to be
quantized at the position sk, k = 0,1,...,$\frac{N-1}{s}$ for even
time instance. Here, s is the gap between two frequencies. For odd
time instances, subcarriers at the position sk + t for k = 0,1,...,
$\frac{N-1}{s}$ with t = ${\frac{s}{2}}$.

@@

One problem associated with the tracking of phases ($\phi$) is that they change abruptly (cite the figure) between $-\pi$ and $\pi$ since $\sin/\cos(\pi) =\sin/\cos(-\pi)$. Therefore we have to wrap around the values by removing those abrupt changes (/cite another figure here).

@@

\subsection{Initial Quantization}
For the first and the second simulations/time instances we use of $\textbf{B}$ = 10 bits for quantizing each parameter for effective quantization/initialization. Therefore, the number of bits for each subcarrier = $10\times12$ = 120. Quantization is performed as given in Section~\ref{section2}.

@@

Initialization is performed by using $10\times12$ bits for each subcarrier for the initial two time frames. Later, the quantization will take place in the time-domain using one bit for each parameter. Since the bit budget is low and we are considering slowly varying channels, therefore, either theta or phi parameters are sent alternatingly in the time domain while keeping the unsent parameters equal to their previous values as show in the Figure \ref{adpm-fig}. Here $\Theta$ is the the collection of all $\theta$'s and $\Phi$ is the collection of all $phi$'s. This brings down the bit budget to average of 5(Size of $\Theta$) and 7(Size of $\Phi$) i.e. 6 bits average per fed back subcarrier.

\bf{ADPM Design}: The decrement rate - \bm is 2.4 times the \bM - increment rate in the Equation~\ref{delta_eqn} . This ratio was decided after trying with different ratios. This implies that if quantied values loose track of the actual values then after changing delta quickly they start following it again.
Also, need to describe the initialization of the Delta values required in the quantization process. Need to cite that paper. We should also try over different quantization rates to compare

@@

>>>>

%% This is a skeleton file demonstrating the use of IEEEtran.cls (requires IEEEtran.cls version 1.8a or later) with an IEEE conference paper.

%%

%% Modified by Khan Reaz( kahn.reaz@ieee.org)

%% Support sites:

%% http://www.ieee.org/

%%***********************************************************

%% Legal Notice:

%% This code is offered as-is without any warranty either expressed or implied; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE!

%% User assumes all risk and can modify as s/he wants.

%%***********************************************************

\def\b0{{\bf 0}}

\def\ba{{\bf a}}

\def\bb{{\bf b}}

\def\bc{{\bf c}}

\def\bd{{\bf d}}

\def\be{{\bf e}}

\def\bg{{\bf g}}

\def\bh{{\bf h}}

\def\bi{{\bf i}}

\def\bj{{\bf j}}

\def\bk{{\bf k}}

\def\bl{{\bf l}}

\def\bm{{\bf m}}

\def\bn{{\bf n}}

\def\bo{{\bf o}}

\def\bp{{\bf p}}

\def\bq{{\bf q}}

\def\br{{\bf r}}

\def\bs{{\bf s}}

\def\bt{{\bf t}}

\def\bu{{\bf u}}

\def\bv{{\bf v}}

\def\bw{{\bf w}}

\def\bx{{\bf x}}

\def\by{{\bf y}}

\def\bz{{\bf z}}

\def\bSigma{{\bf \Sigma}}

\def\bA{{\bf A}}

\def\bB{{\bf B}}

\def\bC{{\bf C}}

\def\bD{{\bf D}}

\def\bE{{\bf E}}

\def\bF{{\bf F}}

\def\bG{{\bf G}}

\def\bH{{\bf H}}

\def\bI{{\bf I}}

\def\bJ{{\bf J}}

\def\bK{{\bf K}}

\def\bL{{\bf L}}

\def\bM{{\bf M}}

\def\bN{{\bf N}}

\def\bO{{\bf O}}

\def\bP{{\bf P}}

\def\bQ{{\bf Q}}

\def\bR{{\bf R}}

\def\bS{{\bf S}}

\def\bT{{\bf T}}

\def\bU{{\bf U}}

\def\bV{{\bf V}}

\def\bW{{\bf W}}

\def\bX{{\bf X}}

\def\bY{{\bf Y}}

\def\bZ{{\bf Z}}

%package list

\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts

\let\labelindent\relax

% \usepackage{breqn}

\usepackage{enumitem}

\usepackage{fleqn}

\usepackage{cite}

\usepackage{graphicx}

\usepackage[varg]{newtxmath}

\graphicspath{ {images/} }

\usepackage{pdfpages}

\usepackage{wrapfig}

\usepackage{fancyhdr}

\usepackage{lastpage}

\usepackage{lettrine}

\usepackage{amsmath}

% \usepackage{titlesec}

\usepackage{mathtools}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage{float}

\usepackage[font={footnotesize}]{caption}

\usepackage[numbers,sort,square,compress]{natbib}

\usepackage[para]{footmisc}

\usepackage{xcolor}

\setlength{\belowcaptionskip}{-12pt}

\newcommand{\highlight}[1]{%

  \colorbox{red!50}{$\displaystyle#1$}}

% \usepackage{parskip}

% \setlength{\parskip}{0.02\baselineskip}

% \fancypagestyle{plain}{

%   \fancyhf{} % sets both header and footer to nothing

% \renewcommand{\headrulewidth}{0pt}

%   \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}% Right header

% }

\pagestyle{plain}% Set page style to plain.

% \pagestyle{fancyplain}

% \fancyhf{}

% \renewcommand{\headrulewidth}{0pt}

% \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}

\DeclareMathOperator*{\argmin}{argmin}

% \usepackage{titlesec}

% \titlespacing*{\section}{0pt}{1pt plus 2p}{1ex}

% \titleformat*{\section}{\fontsize{12}{12}\bfseries}

% \titleformat{\section}

%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries}{\thesection}{1em}{}

% \titleformat{\subsection}

%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries\itshape}{\thesubsection}{1em}{}

\begin{document}

%Here goes the title

@@

\author{\authorblockN{Author 1, Author 2, Author 3}

\

\authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay}

% \thanks{Parts of this work was supported by the Bharti Centre for Communication in

% Government of India (implemented by the Digital India Corporation).

% }}

}

\maketitle

\thispagestyle{plain}

%Main body starts

% \noindent We consider problem of quantization and interpolation of

% time and frequency varying precoding matrices in wireless MIMO

\begin{abstract}

In a limited feedback MIMO channel, the performance of the channel can improve significantly if the transmitter knows the channel state information (CSI). The receiver knows the channel information, and it feeds back to the transmitter. However, it is not possible to feedback complete information for a limited-feedback OFDM channel since the channel information for multiple subcarriers consumes a large amount of data. Therefore, to resolve this problem, the orthonormality structure of the precoder matrix is exploited to make its one-to-one mapping to a minimal number of scalar parameters. The Precoder matrix is decomposed using Givens Rotation. For an i.i.d. flat-fading Rayleigh channel, these parameters are independent, which makes its quantization and interpolation easy. We propose an efficient method for quantization of the channel state information at the receiver by using adaptive delta modulation for successive time interval. We also propose a method for joint time-frequency interpolation of the channel information at the transmitter.

\end{abstract}

@@

The use of multiple antennas at the transmitter and receiver can significantly enhance the performance of wireless systems. Moreover, in these multiple-input multiple-output (MIMO) wireless systems, the transmitter can perform better resource allocation if channel state information (CSI) is made available at the transmitter, both to improve data rates and reduce BER~\cite{love2008overview}. To this end, feeding back the channel state information from the receiver to the transmitter efficiently is necessary. In the many wireless systems that use orthogonal frequency division multiplexing (OFDM), the feedback needs to be provided to the transmitter across the many subcarriers of the system, which places a large feedback demand. However, since the channel state information varies gradually in both time and frequency, effective techniques to reduce feedback overheads exist, using frequency interpolation temporal prediction. In particular, knowledge of the precoding matrices (that are typically the orthonormal right singular vectors of the channel matrix) is essential to enable the transmitter to transmit at capacity as well as to parallelize the channel. In this paper, we focus on the problem of tracking the precoders of a MIMO-OFDM system across time and frequency for efficient CSI feedback.

% TODO More coverage of prior work needed.

The problem of effective quantization and feedback of precoders for MIMO-OFDM attracted significant attention In recent years. Many approaches involve codebook design over the Stiefel Manifold \cite{6891198}, wherein the manifold structure of the precoders is used to obtain tangents for predictive quantization and interpolation across time and frequency. Another such variation of \cite{6891198} has exploited both time and frequency domain together in Stiefel Manifold \cite{Gupt1905:Predictive}. All these methods are useful, but they do so over Manifolds which has problems of getting stuck in local Maxima. Also, there are different challenged which are faced while interpolating in a high dimensional space.

Other approaches have considered the problem of parametrizing precoding matrices using scalar parameters. It has been shown that the space of unitary matrices can be effectively parameterized using scalar parameters that correspond to Givens rotations and Household Transformations of the unitary precoding matrices \cite{4114278,4556174}. By tracking these scalar parameters using adaptive digital pulse code modulation (ADPCM) for slowly varying channels in the time domain and the frequency domain, the link can operate close to capacity while using very few bits for quantization and feedback.

We now propose a method for predictive quantization in time domain over few subcarriers using scalar parameters. We also propose a method for exploiting the joint time-frequency correlation of those scalar parameters on the transmitter side. In \ref{section2}, we start by explaining the system model and the method for scalar quantization \& interpolation of the precoder matrix. In \ref{section3}, we perform various simulations for our approach and show the benefits from the improved BER rates and Achievable Rate.

@@

\begin{equation} 
y_{i,t} = H_{i,t} x_{i,t}+ \eta 
\end{equation}

@@

where the channel matrix $H_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $x_{i,t} \in \mathbb{C}^{N_T}$; the output $y_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $H_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_T}$, $\Sigma_{i,t} \in \mathbb{C}^{N_T \times N_T}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_T}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

% Givens rotation definition and how we are decomposing, Theta- pdf = 2lsin(theta)(2l-1).cos(theta) 0 $\leq$ Theta $\leq$ pi/2. 
% Householders' transformation and how we are decomposing. -pi$\leq$ phi $\leq$ pi. Uniformly distributed. 
% Low-complexity quantization scheme based on a further parameterization of a vector in 
% terms of a minimal number of independent scalar parameters. In particular, we consider its application to CSI feedback in slowly time-varying MIMO channels

@@

I_{m-2} & & & \\ 
& cos\;\theta & - sin\;\theta & \\ 
& sin\;\theta & cos\;\theta & \\ 
& & & I_{t-m}

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{images/adpm.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

\begin{equation} 
p(\theta) = 2lsin(\theta)^{2l-1}cos(\theta), \theta \in [0, \frac{\pi}{2}), for \; l = 1,2,\ldots,t-1
\end{equation}

@@

\begin{equation} 
\Delta_{n} = \begin{cases} 
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}.\\ 
    \Delta_{n-1}/m , & \text{if $\beta_{n} \neq \beta_{n-1}$}. 
  \end{cases} 
\end{equation}

@@

We need to quantize the subcarriers in a way such that we can exploit the joint time-frequency interpolation at the transmitter side. Therefore, we select the subcarriers for quantization in an alternating fashion as shown in the figure. Figure shows a \textbf{N} subcarrier MIMO channel with subcarriers which are going to be quantized at the position sk, k = 0,1,...,$\frac{N-1}{s}$ for even time instance. Here, s is the gap between two frequencies. For odd time instances, subcarriers at the position sk + t for k = 0,1,..., $\frac{N-1}{s}$ with t = $\floor*{\frac{s}{2}}$.

@@

One problem associated with the tracking of phases ($\phi$) is that they change abruptly (cite the figure) between $-\pi$ and $\pi$ since $sin/cos(\pi) = sin/cos(-\pi)$. Therefore we have to wrap around the values by removing those abrupt changes (/cite another figure here).

@@

\subsection{Initial Quantization} 
For the first and the second simulations/time instances we use of $\textbf{B}$ = 10 bits for quantizing each parameter for effective quantization/initialization. Therefore, the number of bits for each subcarrier = $10\times12$ = 120. Quantization is performed as given in \ref{section2}.

@@

Initialization is performed by using $10\times12$ bits for each subcarrier for the initial two time frames. Later, the quantization will take place in the time-domain using one bit for each parameter. Since the bit budget is low and we are considering slowly varying channels, therefore, we will be sending either theta or phi parameters alternatingly in the time domain while keeping the unsent parameters equal to their previous values. This brings down the bit budget to 6 bits average per fed back subcarrier.

Describing how you performed ADPCM to carry out the 1-bit quantization. Also, the increment rate was 2.4 times the decay rate. Also, need to describe the initialization of the Delta values required in the quantization process. I need to cite that paper. We should also try over different quantization rates to compare \cite{Gupt1905:Predictive}

@@

% Remove the first para of FSM. State what r1,r2,d,\theta are in the FSM model states themselves. As a concluding statement of STAT-2 state that using the

% inherit geometery of the problem, we get AoA
